|

### 2023-05-19 manuscript/paper.Rmd
Adding bib.
update

>>>>

@LeeFort2008: Attendance and the Uncertainty-of-Outcome Hypothesis in Baseball.  Identify Break points in attendance in 1918 and 1945 for both leagues.  For AL only: 1963, 1978, 1994.  For NL only: 1976.  Using Bai and Perron From table 3 in Mills and Fort 2014
@MillsFort2014: LEAGUE-LEVEL ATTENDANCE AND OUTCOME UNCERTAINTY IN U.S. PRO SPORTS LEAGUES.  Looks at NHL, NFL, NBA.  Rottenburg 1956 looked at baseball.  Identify break points in NBA, NFL, and NHL.  Table 3
@MillsSalaga2015: NCAA Basketball: League balance using stats.  
@MillsFort2018: team-level: Attendence.  
@SalagaFort2017: College football
